### 2018-09-04 practice-proofs/EH4.tex
Added files for practice proofs 4-9.

We explicitly construct a bijection mapping from the unit interval to the whole real line.

\begin{thm} \label{thm:BijectionRInterval}
	Define $f : (0,1) \to \RR$ by
	$$
		f(x) =\frac{1}{1-x} - \frac{1}{x}.
	$$
	The function $f$ is a bijection.
\end{thm}

\hintbox{
	If you can show that $f$ is strictly increasing, then that should give you injectivity.

	For surjectivity, you need to justify that, for every real number $y$, there is some $x\in(0,1)$ such that $f(x)=y$.
	The idea is to consider, for large $M>0$, $f(1/M)$ and $f(1-1/M)$ show that these are large positive and negative numbers, respectively.
	Then you can use the intermediate value theorem to conclude that because, for some $M$, $f(1/M)<y<f(1-1/M)$, the required $x$ must exist.
}

### 2018-09-04 practice-proofs/EH5.tex
Added files for practice proofs 4-9.

\subsection*{Cardinality and subsets}

\begin{prop} \label{prop:SubsetCardinality}
	If $X\subset Y$, then $\# X\leq \# Y$.
\end{prop}

\hintbox{
	Directly construct an injection $f:X\to Y$.
	If the codomain of $f$ was $X$, then you could choose a bijection quite easily.
	What happens if you expand the codomain back to $Y$?
}

\subsection*{Countable unions of sets}

We study the cardinality of ordinary and disjoint unions of countable sets.

\begin{lem} \label{lem:CountableUnions1}
	If $\#A=\#B=\aleph_0$, then $\#(A\times B)=\aleph_0$.
\end{lem}

\hintbox{
	Stitch together some bijections that must exist, to produce a useful bijection.
}

\begin{prop} \label{prop:CountableUnions2}
	If, for each $j\in J$, $A_j$ is a nonempty set with cardinality $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
	$$
		\# \bigsqcup_{j\in J} A_j = \aleph_0.
	$$
\end{prop}

\hintbox{
	Start by recalling the definition of disjoint union.
	Find separately an injection and a surjection to the disjoint union of interest, and use the CSB theorem.

	Can you find a surjection from $\NN\times J$ to the disjoint union?

	Note that we asked for all $A_j$ to be nonempty.
	What would happen if all (or all but finitely many) $A_j$ were $\emptyset$?
	This offers a clue to how an injection might be constructed.
}

\begin{prop} \label{prop:CountableUnions3}
	If, for each $j\in J$, $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
	$$
		\# \bigcup_{j\in J} A_j \leq \aleph_0.
	$$
\end{prop}

\hintbox{
	Direct construction of a surjection from the disjoint union of the previous proposition to this ordinary union.
}

\subsection*{Cardinality and power sets}

We say that two sets are \emph{equinumerous} if they have the same cardinality. The following proposition says that the operation ``take the power set'' preserves equinumerosity.

\begin{prop} \label{prop:PowerSetsPreserveEquinumerosity}
	Suppose $\# X=\# Y$. Then $\# \power(X)=\# \power(Y)$. Moreover, if $\# X\leq\# Y$, then $\# \power(X)\leq\# \power(Y)$.
\end{prop}

\hintbox{
	There must be a bijection $f:X\to Y$. Pick an arbitrary $S\subset X$.
	Think about the process of taking the image of $S$ in $f$.
	Is that a function of $S$? Showing injectivity / surjectivity requires you to exploit injectivity / surjectivity of $f$.

	It is probably more efficient to prove the second part first.
}

### 2018-09-04 practice-proofs/EH6.tex
Added files for practice proofs 4-9.

--- 2018-09-04 practice-proofs/EH5.tex
@@
-\subsection*{Cardinality and subsets}
-
-\begin{prop} \label{prop:SubsetCardinality}
-	If $X\subset Y$, then $\# X\leq \# Y$.
-\end{prop}
-
-\hintbox{
-	Directly construct an injection $f:X\to Y$.
-	If the codomain of $f$ was $X$, then you could choose a bijection quite easily.
-	What happens if you expand the codomain back to $Y$?
-}
-
-\subsection*{Countable unions of sets}
-
 We study the cardinality of ordinary and disjoint unions of countable sets.
 
-\begin{lem} \label{lem:CountableUnions1}
+\begin{lem} \label{lem:CardinalityUnions1}
 	If $\#A=\#B=\aleph_0$, then $\#(A\times B)=\aleph_0$.
@@
 
-\begin{prop} \label{prop:CountableUnions2}
+\begin{prop} \label{prop:CardinalityUnions2}
 	If, for each $j\in J$, $A_j$ is a nonempty set with cardinality $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
@@
 
-\begin{prop} \label{prop:CountableUnions3}
+\begin{prop} \label{prop:CardinalityUnions3}
 	If, for each $j\in J$, $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
@@
 \hintbox{
-	Direct construction of a surjection from the disjoint union of the previous proposition to this ordinary union.
+	Direct construction of a surjection from the disjoint union appearing in proposition~\ref{prop:CardinalityUnions2} to this ordinary union.
 }
-
-\subsection*{Cardinality and power sets}
-
-We say that two sets are \emph{equinumerous} if they have the same cardinality. The following proposition says that the operation ``take the power set'' preserves equinumerosity.
-
-\begin{prop} \label{prop:PowerSetsPreserveEquinumerosity}
-	Suppose $\# X=\# Y$. Then $\# \power(X)=\# \power(Y)$. Moreover, if $\# X\leq\# Y$, then $\# \power(X)\leq\# \power(Y)$.
-\end{prop}
-
-\hintbox{
-	There must be a bijection $f:X\to Y$. Pick an arbitrary $S\subset X$.
-	Think about the process of taking the image of $S$ in $f$.
-	Is that a function of $S$? Showing injectivity / surjectivity requires you to exploit injectivity / surjectivity of $f$.
-
-	It is probably more efficient to prove the second part first.
-}

### 2018-09-04 practice-proofs/EH7.tex
Added files for practice proofs 4-9.

Here we take for granted the set of integers, and all familiar properties of addition, subtraction, and multiplication of integers.
We also take for granted the ``integral domain'' property of integers, which states that $xy = 0$ implies $x = 0$ or $y = 0$, for all integers $x,y$.
Equivalently, if $x \neq 0$ and $y \neq 0$ then $xy \neq 0$.
This implies the cancellation property: if $x,y,z \in \ZZ$, and $z \neq 0$, and $xz = yz$, then $x = y$.

A \emph{fraction} will mean an ordered pair $(x,y) \in \ZZ^2$ such that $y \neq 0$. Let $F$ be the set of fractions. Consider the relation $\sim$ on $F$ given by the rule
$$
	(x,y) \sim (u,v) \text{ means that } xv = yu.
$$
The point of $\sim$ is that if two fractions obey $(x,y)\sim(u,v)$, then they are two expressions of the same rational number.
For example, $(2,4)\sim(12,24)$, and they both correspond to the rational number that we are used to representing $\frac{1}{2}$.

\begin{thm} \label{thm:EquivaentFractions}
	The relation $\sim$ is an equivalence relation on the set $F$.
\end{lem}

\hintbox{
	Direct proof that $\sim$ satisfies each of the three properties of an equivalence relation.
	Reflexivity and Symmetry are direct proofs, no more than 2 lines each.
	Transitivity requires a little more care, to avoid dividing by $0$.
}

### 2018-09-04 practice-proofs/EH8.tex
Added files for practice proofs 4-9.

We aim to construct real numbers as equivalence classes of rational Cauchy sequences.
We will eventually have to show that adding and multiplying real numbers produces real numbers (see the field axioms), so it would help to know that adding and multiplying the underlying objects, rational Cauchy sequences, produces more rational Cauchy sequences.

\begin{prop} \label{prop:RationalCauchyClosedUnderSum}
	Suppose that $(a_n)_{n\in\NN}$ and $(b_n)_{n\in\NN}$ are both rational Cauchy sequences.
	Then $(a_n+b_n)_{n\in\NN}$ is also a rational Cauchy sequence.
\end{prop}

\hintbox{
	In the definition of a Cauchy sequence, replace the symbol $\epsilon$ with the symbol $\delta$, and $N(\epsilon)$ with $N_a(\delta)$ for the first sequence and $N_b(\delta)$ for the second, and write down these statements.
	Write down the statement you are trying to prove (i.e.\ the definition of a Cauchy sequence).
	Try using the triangle inequality on $|(a_m+b_m) - (a_n+b_n)|$ to bound it in terms of something you know about.
	Now choose $N(\epsilon)$, with reference to $N_a$ and $N_b$, in such a way that you can ensure $|(a_m+b_m) - (a_n+b_n)|<\epsilon$.
}

### 2018-09-04 practice-proofs/EH9.tex
Added files for practice proofs 4-9.

We argue that real multiplication, as defined through multiplication of rational Cauchy sequences, satisfies the corresponding five field axioms.

\begin{lem} \label{lem:ExistsNonzeroCauchySequence}
	Suppose that $x\in\RR\setminus\{0_\RR\}$.
	Then there is a rational $M>0$ and a Cauchy sequence $(x_n)_{n\in\NN}$ such every term has $|x_n|>M$ and $(x_n)_{n\in\NN}$ belongs to the equivalence class $x$.
\end{lem}

\hintbox{
	The idea is to argue that, for each rational $M>0$, there is a rational Cauchy sequence in $x$ for which at most finitely many terms are less than $M$.
	Try contradiction.
	Begin by assuming that $(a_n)_{n\in\NN}$ is a rational Cauchy sequence in $x$ for which infinitely many terms are $M$.
	You should end up proving $x=0_\RR$ for the contradiction.

	Now you know there is a rational Cauchy sequence in $x$ with at most finitely many ``problem'' terms that are less than $M$.
	Fix each of the problem terms by changing them to something else.
}

\begin{thm} \label{thm:RealMultiplication}
	Real multiplication, defined as the descent of multiplication of rational Cauchy sequences, obeys field axioms~\textup{(6)--(10)}.
\end{thm}

\hintbox{
	Axioms~(6)--(9) essentially follow from the corresponding properties for rational numbers.
	For each axiom, you will need to start with real numbers, define representative rational Cauchy sequences, combine your rational Cauchy sequences in the appropriate way, then map back to the real numbers.

	For axiom~(10), the method is essentially the same, but when you produce your new rational Cauchy sequence $(y_n)_{n\in\NN}$ (which will represent the real multiplicative inverse of $(x_n)_{n\in\NN}$) it is not so simple to prove that it is actually Cauchy.
	It might be easiest to start by structuring the proof as if you have a magical lemma that guarantees $(y_n)_{n\in\NN}$ is Cauchy.
	After you have the main proof worked out, go back and fill in the ``$(y_n)_{n\in\NN}$ is Cauchy'' gap. When studying $|y_n-y_m|$, try multiplying and dividing by $|x_n||x_m|$. You will need to use lemma~\ref{lem:ExistsNonzeroCauchySequence}.
}

### 2018-09-04 practice-proofs/PracticeProofs4.tex
Added files for practice proofs 4-9.

%---------DO NOT EDIT THIS INDENTED SECTION
	% Preamble
	\documentclass[11pt,reqno,oneside,a4paper]{article}
	\usepackage[a4paper,includeheadfoot,left=35mm,right=35mm,top=00mm,bottom=30mm,headheight=40mm]{geometry} %sets up the margins
	\input{../texHead-Proof-Standard} % Use the standard texHead for this module. You should not edit this file.
	\input{../texHead-Proof-Personal} % Use your personal additional macros. You may edit this file.
	%---The following code defines the title, author, and date of the document.
	\title{Practice proofs \#4}
	\author{Anonymous}
	\date{\today}   % Using \today automatically updates to the document's build date
%----------------------------------
%---------IF YOU WANT TO DEFINE YOUR OWN MACROS, YOU CAN DO SO EITHER IN ../texHead-Proof-Personal.tex OR FROM HERE ...

%---------... TO HERE
\begin{document}
\maketitle
\thispagestyle{fancy}

%-----------EDIT FROM HERE

\begin{abstract}
	\input{PracticeProofsStandardAbstract.tex}

	I fitted the whole model solutions onto a little over 1 page.
\end{abstract}

We explicitly construct a bijection mapping from the unit interval to the whole real line.

\begin{thm} \label{thm:BijectionRInterval}
	Define $f : (0,1) \to \RR$ by
	$$
		f(x) =\frac{1}{1-x} - \frac{1}{x}.
	$$
	The function $f$ is a bijection.
\end{thm}

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Prove that $f$ is both a surjection and an injection.
	% It will help to show that $f$ is strictly increasing.
	% The intermediate value theorem is also important; if you have not seen it before, then look it up.
	%------------------------------------------%
\end{proof}

\end{document}

### 2018-09-04 practice-proofs/PracticeProofs5.tex
Added files for practice proofs 4-9.

--- 2018-09-04 practice-proofs/EH5.tex
@@
+%---------DO NOT EDIT THIS INDENTED SECTION
+	% Preamble
+	\documentclass[11pt,reqno,oneside,a4paper]{article}
+	\usepackage[a4paper,includeheadfoot,left=35mm,right=35mm,top=00mm,bottom=30mm,headheight=40mm]{geometry} %sets up the margins
+	\input{../texHead-Proof-Standard} % Use the standard texHead for this module. You should not edit this file.
+	\input{../texHead-Proof-Personal} % Use your personal additional macros. You may edit this file.
+	%---The following code defines the title, author, and date of the document.
+	\title{Practice proofs \#5}
+	\author{Anonymous}
+	\date{\today}   % Using \today automatically updates to the document's build date
+%----------------------------------
+%---------IF YOU WANT TO DEFINE YOUR OWN MACROS, YOU CAN DO SO EITHER IN ../texHead-Proof-Personal.tex OR FROM HERE ...
+
+%---------... TO HERE
+\begin{document}
+\maketitle
+\thispagestyle{fancy}
+
+%-----------EDIT FROM HERE
+
+\begin{abstract}
+	\input{PracticeProofsStandardAbstract.tex}
+
+	I fitted the whole model solutions onto $1.5$ pages.
+\end{abstract}
+
 \subsection*{Cardinality and subsets}
@@
 
-\hintbox{
-	Directly construct an injection $f:X\to Y$.
-	If the codomain of $f$ was $X$, then you could choose a bijection quite easily.
-	What happens if you expand the codomain back to $Y$?
-}
+\begin{proof}
+	%--------------EDIT THIS PART--------------%
+	% Hint: Directly construct an injection.
+	%------------------------------------------%
+\end{proof}
 
@@
 
-\hintbox{
-	Stitch together some bijections that must exist, to produce a useful bijection.
-}
+\begin{proof}
+	%--------------EDIT THIS PART--------------%
+	% Hint: Direct proof.
+	%------------------------------------------%
+\end{proof}
 
@@
 
-\hintbox{
-	Start by recalling the definition of disjoint union.
-	Find separately an injection and a surjection to the disjoint union of interest, and use the CSB theorem.
-
-	Can you find a surjection from $\NN\times J$ to the disjoint union?
-
-	Note that we asked for all $A_j$ to be nonempty.
-	What would happen if all (or all but finitely many) $A_j$ were $\emptyset$?
-	This offers a clue to how an injection might be constructed.
-}
+\begin{proof}
+	%--------------EDIT THIS PART--------------%
+	% Hint: Start by recalling the definition of disjoint union. Find separately an injection and a surjection to the disjoint union of interest, and use the CSB theorem.
+	%------------------------------------------%
+\end{proof}
 
@@
 
-\hintbox{
-	Direct construction of a surjection from the disjoint union of the previous proposition to this ordinary union.
-}
+\begin{proof}
+	%--------------EDIT THIS PART--------------%
+	% Hint: Direct construction.
+	%------------------------------------------%
+\end{proof}
 
@@
 
-\hintbox{
-	There must be a bijection $f:X\to Y$. Pick an arbitrary $S\subset X$.
-	Think about the process of taking the image of $S$ in $f$.
-	Is that a function of $S$? Showing injectivity / surjectivity requires you to exploit injectivity / surjectivity of $f$.
+\begin{proof}
+	%--------------EDIT THIS PART--------------%
+	% Hint: There must be a bijection $f:X\to Y$. Pick an arbitrary $S\subset X$. Think about the process of taking the image of $S$ in $f$. Is that a function of $S$?
+	%------------------------------------------%
+\end{proof}
 
-	It is probably more efficient to prove the second part first.
-}
+\end{document}

### 2018-09-04 practice-proofs/PracticeProofs6.tex
Added files for practice proofs 4-9.

--- 2018-09-04 practice-proofs/PracticeProofs5.tex
@@
 	%---The following code defines the title, author, and date of the document.
-	\title{Practice proofs \#5}
+	\title{Practice proofs \#6}
 	\author{Anonymous}
@@
 
-	I fitted the whole model solutions onto $1.5$ pages.
+	I fitted the whole model solutions onto 1 page.
 \end{abstract}
-
-\subsection*{Cardinality and subsets}
-
-\begin{prop} \label{prop:SubsetCardinality}
-	If $X\subset Y$, then $\# X\leq \# Y$.
-\end{prop}
-
-\begin{proof}
-	%--------------EDIT THIS PART--------------%
-	% Hint: Directly construct an injection.
-	%------------------------------------------%
-\end{proof}
-
-\subsection*{Countable unions of sets}
 
@@
 
-\begin{lem} \label{lem:CountableUnions1}
+\begin{lem} \label{lem:CardinalityUnions1}
 	If $\#A=\#B=\aleph_0$, then $\#(A\times B)=\aleph_0$.
@@
 	%--------------EDIT THIS PART--------------%
-	% Hint: Start by recalling the definition of disjoint union. Find separately an injection and a surjection to the disjoint union of interest, and use the CSB theorem.
+	% Hint: Start by recalling the definition of disjoint union.
+	% Find separately an injection and a surjection to the disjoint union of interest, and use the CSB theorem.
 	%------------------------------------------%
@@
 
-\subsection*{Cardinality and power sets}
-
-We say that two sets are \emph{equinumerous} if they have the same cardinality. The following proposition says that the operation ``take the power set'' preserves equinumerosity.
-
-\begin{prop} \label{prop:PowerSetsPreserveEquinumerosity}
-	Suppose $\# X=\# Y$. Then $\# \power(X)=\# \power(Y)$. Moreover, if $\# X\leq\# Y$, then $\# \power(X)\leq\# \power(Y)$.
-\end{prop}
-
-\begin{proof}
-	%--------------EDIT THIS PART--------------%
-	% Hint: There must be a bijection $f:X\to Y$. Pick an arbitrary $S\subset X$. Think about the process of taking the image of $S$ in $f$. Is that a function of $S$?
-	%------------------------------------------%
-\end{proof}
-
 \end{document}

### 2018-09-04 practice-proofs/PracticeProofs7.tex
Added files for practice proofs 4-9.

--- 2018-09-04 practice-proofs/PracticeProofs4.tex
@@
 	%---The following code defines the title, author, and date of the document.
-	\title{Practice proofs \#4}
+	\title{Practice proofs \#7}
 	\author{Anonymous}
@@
 
-	I fitted the whole model solutions onto a little over 1 page.
+	I fitted the whole model solutions onto $4/3$ pages.
 \end{abstract}
 
-We explicitly construct a bijection mapping from the unit interval to the whole real line.
+Here we take for granted the set of integers, and all familiar properties of addition, subtraction, and multiplication of integers.
+We also take for granted the ``integral domain'' property of integers, which states that $xy = 0$ implies $x = 0$ or $y = 0$, for all integers $x,y$.
+Equivalently, if $x \neq 0$ and $y \neq 0$ then $xy \neq 0$.
+This implies the cancellation property: if $x,y,z \in \ZZ$, and $z \neq 0$, and $xz = yz$, then $x = y$.
 
-\begin{thm} \label{thm:BijectionRInterval}
-	Define $f : (0,1) \to \RR$ by
+A \emph{fraction} will mean an ordered pair $(x,y) \in \ZZ^2$ such that $y \neq 0$. Let $F$ be the set of fractions.
+Consider the relation $\sim$ on $F$ given by the rule
 $$
-		f(x) =\frac{1}{1-x} - \frac{1}{x}.
+	(x,y) \sim (u,v) \text{ means that } xv = yu.
 $$
-	The function $f$ is a bijection.
+The point of $\sim$ is that if two fractions obey $(x,y)\sim(u,v)$, then they are two expressions of the same rational number.
+For example, $(2,4)\sim(12,24)$, and they both correspond to the rational number that we are used to representing $\frac{1}{2}$.
+
+\begin{thm} \label{thm:EquivaentFractions}
+	The relation $\sim$ is an equivalence relation on the set $F$.
 \end{thm}
@@
 	%--------------EDIT THIS PART--------------%
-	% Prove that $f$ is both a surjection and an injection.
-	% It will help to show that $f$ is strictly increasing.
-	% The intermediate value theorem is also important; if you have not seen it before, then look it up.
+	% Hint: Direct proof that $\sim$ satisfies each of the three properties of an equivalence relation.
 	%------------------------------------------%

### 2018-09-04 practice-proofs/PracticeProofs8.tex
Added files for practice proofs 4-9.

%---------DO NOT EDIT THIS INDENTED SECTION
	% Preamble
	\documentclass[11pt,reqno,oneside,a4paper]{article}
	\usepackage[a4paper,includeheadfoot,left=35mm,right=35mm,top=00mm,bottom=30mm,headheight=40mm]{geometry} %sets up the margins
	\input{../texHead-Proof-Standard} % Use the standard texHead for this module. You should not edit this file.
	\input{../texHead-Proof-Personal} % Use your personal additional macros. You may edit this file.
	%---The following code defines the title, author, and date of the document.
	\title{Practice proofs \#8}
	\author{Anonymous}
	\date{\today}   % Using \today automatically updates to the document's build date
%----------------------------------
%---------IF YOU WANT TO DEFINE YOUR OWN MACROS, YOU CAN DO SO EITHER IN ../texHead-Proof-Personal.tex OR FROM HERE ...

%---------... TO HERE
\begin{document}
\maketitle
\thispagestyle{fancy}

%-----------EDIT FROM HERE

\begin{abstract}
	\input{PracticeProofsStandardAbstract.tex}
	Also delete the (completed for you!)\ proof of proposition~\ref{prop:RationalCauchyClosedUnderProduct} before submitting.

	I fitted the whole model solutions onto $3/4$ of a page.
\end{abstract}

We aim to construct real numbers as equivalence classes of rational Cauchy sequences.
We will eventually have to show that adding and multiplying real numbers produces real numbers (see the field axioms), so it would help to know that adding and multiplying the underlying objects, rational Cauchy sequences, produces more rational Cauchy sequences.

\begin{prop} \label{prop:RationalCauchyClosedUnderSum}
	Suppose that $(a_n)_{n\in\NN}$ and $(b_n)_{n\in\NN}$ are both rational Cauchy sequences.
	Then $(a_n+b_n)_{n\in\NN}$ is also a rational Cauchy sequence.
\end{prop}

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: In the definition of a Cauchy sequence, replace the symbol $\epsilon$ with the symbol $\delta$, and $N(\epsilon)$ with $N_a(\delta)$ for the first sequence and $N_b(\delta)$ for the second.
	% Write down the statement you are trying to prove (i.e.\ the definition of a Cauchy sequence).
	% Try using the triangle inequality and choosing $N$ in a clever way.
	%------------------------------------------%
\end{proof}

\begin{prop} \label{prop:RationalCauchyClosedUnderProduct}
	Suppose that $(a_n)_{n\in\NN}$ and $(b_n)_{n\in\NN}$ are both rational Cauchy sequences.
	Then $(a_nb_n)_{n\in\NN}$ is also a rational Cauchy sequence.
\end{prop}

\begin{proof}
	The rational numbers are closed under multiplication, so $(a_nb_n)_{n\in\NN}$ is a rational sequence.

	As both of the original sequences are Cauchy, they are both bounded.
	So we can choose a positive rational number $M$ that is a common bound for both sequences, in the sense that, for all $n\in\NN$, $|a_n|,|b_n|<M$.
	Let $\delta>0$.
	Then there exist natural numbers $N_a(\delta),N_b(\delta)$ such that
	\begin{align*}
		&\mbox{if } m,n > N_a(\delta), \mbox{ then } |a_m-a_n|<\delta, \\
		&\mbox{if } m,n > N_b(\delta), \mbox{ then } |b_m-b_n|<\delta.
	\end{align*}
	Suppose $\epsilon>0$, set $N=\max\{N_a(\epsilon/2M),N_b(\epsilon/2M)\}$, and suppose that $m,n>N$.
	Then
	\begin{align*}
		|(a_mb_m) - (a_nb_n)| &= |(a_m-a_n)b_m + a_n(b_m-b_n)| \\
		&\leq |a_m-a_n||b_m| + |a_n||b_m-b_n| \\
		&< \frac{\epsilon}{2M}M + M\frac{\epsilon}{2M} = \epsilon.
	\end{align*}
	Therefore the sequence $(a_nb_n)_{n\in\NN}$ is Cauchy.
\end{proof}

\end{document}

### 2018-09-04 practice-proofs/PracticeProofs9.tex
Added files for practice proofs 4-9.

--- 2018-09-04 practice-proofs/PracticeProofs4.tex
@@
 	%---The following code defines the title, author, and date of the document.
-	\title{Practice proofs \#4}
+	\title{Practice proofs \#9}
 	\author{Anonymous}
@@
 
-	I fitted the whole model solutions onto a little over 1 page.
+	I fitted the whole model solutions onto 2 pages.
 \end{abstract}
 
-We explicitly construct a bijection mapping from the unit interval to the whole real line.
+We argue that real multiplication, as defined through multiplication of rational Cauchy sequences, satisfies the corresponding five field axioms.
 
-\begin{thm} \label{thm:BijectionRInterval}
-	Define $f : (0,1) \to \RR$ by
-	$$
-		f(x) =\frac{1}{1-x} - \frac{1}{x}.
-	$$
-	The function $f$ is a bijection.
+\begin{lem} \label{lem:ExistsNonzeroCauchySequence}
+	Suppose that $x\in\RR\setminus\{0_\RR\}$.
+	Then there is a rational $M>0$ and a Cauchy sequence $(x_n)_{n\in\NN}$ such every term has $|x_n|>M$ and $(x_n)_{n\in\NN}$ belongs to the equivalence class $x$.
+\end{lem}
+
+\begin{proof}
+	%--------------EDIT THIS PART--------------%
+	% Hint: The idea is to argue that there is a rational Cauchy sequence in $x$ for which at most finitely many terms are less than $M$.
+	% Try contradiction; you should end up proving $x=0_\RR$.
+	% After that, you can fix the finitely many ``problem'' terms without changing the equivalence class of your Cauchy sequence.
+	%------------------------------------------%
+\end{proof}
+
+\begin{thm} \label{thm:RealMultiplication}
+	Real multiplication, defined as the descent of multiplication of rational Cauchy sequences, obeys field axioms~\textup{(6)--(10)}.
 \end{thm}
@@
 	%--------------EDIT THIS PART--------------%
-	% Prove that $f$ is both a surjection and an injection.
-	% It will help to show that $f$ is strictly increasing.
-	% The intermediate value theorem is also important; if you have not seen it before, then look it up.
+	% Hint: Axioms~(6)--(9) essentially follow from the corresponding properties for rational numbers.
+	% For axiom~(10), the tricky part is showing that the sequence you want to represent the multiplicative inverse is actually a Cauchy sequence.
+	% It might be easiest to start by structuring the proof as if you have a magical lemma that guarantees the sequence is Cauchy, then go back and fill the gap, using lemma~\ref{lem:ExistsNonzeroCauchySequence} and some ingenuity.
 	%------------------------------------------%

### 2018-09-04 practice-proofs/PracticeProofsExtraHints.tex
Added files for practice proofs 4-9.

%---------DO NOT EDIT THIS FILE
% Preamble
\documentclass[11pt,reqno,oneside,a4paper]{article}
\usepackage[a4paper,includeheadfoot,left=35mm,right=35mm,top=00mm,bottom=30mm,headheight=40mm]{geometry} %sets up the margins
\input{../texHead-Proof-Standard} % Use the standard texHead for this module. You should not edit this file.
\newcommand{\hintbox}[1]{\noindent\fbox{\begin{minipage}[t]{1.0\linewidth} \begin{hint}#1\end{hint} \end{minipage}}\clearpage}

\title{Extra hints for practice proofs}
\author{}
\date{\today}

\begin{document}
\maketitle
\thispagestyle{fancy}

This document will contain extra hints for all the practice proofs, beginning at practice proofs 4.
If it is ever out of date, please \href{mailto:\InstEmail ?subject=Please update 'Extra hints for practice proofs'}{email the instructor} to ask for an update.

\tableofcontents
\clearpage

\setcounter{section}{3}
\section{Practice proofs 4} \input{EH4} \setcounter{thm}{0}
\section{Practice proofs 5} \input{EH5} \setcounter{thm}{0}
\section{Practice proofs 6} \input{EH6} \setcounter{thm}{0}
\section{Practice proofs 7} \input{EH7} \setcounter{thm}{0} \clearpage
\section{Practice proofs 8} \input{EH8} \setcounter{thm}{0} \clearpage
\section{Practice proofs 9} \input{EH9} \setcounter{thm}{0} \clearpage

\end{document}

### 2018-09-04 practice-proofs/PracticeProofsStandardAbstract.tex
Added files for practice proofs 4-9.

%---------DO NOT EDIT THIS FILE

The following exercise is meant to be challenging.
It is expected that your submission will not be perfect, but you will receive feedback on your submission so that you can improve it.
You \textbf{must} complete this exercise entirely on your own.
Do \textbf{not} collaborate with your peers on this exercise.
Do \textbf{not} ask the tutors for help, or search books / web for assistance.
There are hints in the .tex file.
There are more hints in the document \href{run:./PracticeProofsExtraHints.pdf}{PracticeProofsExtraHints.pdf}.
If you need help, please contact Dave by email: \href{mailto:\InstEmail}{\nolinkurl{\InstEmail}}.

You will be graded on participation.
That means it is OK to not have perfect answers, but you will get more out of the exercise if you try your best.

Be sure not to put your name anywhere on the document.
{\color{red}Before submitting, please delete the begin \& end abstract tags and everything between them.}

### 2018-09-07 paper1.tex
Added the Paper 1 file

%---------DO NOT EDIT THIS INDENTED SECTION
	% Preamble
	\documentclass[11pt,reqno,oneside,a4paper]{article}
	\usepackage[a4paper,includeheadfoot,left=35mm,right=35mm,top=00mm,bottom=30mm,headheight=40mm]{geometry} %sets up the margins
	\input{../texHead-Proof-Standard} % Use the standard texHead for this module. You should not edit this file.
	\input{../texHead-Proof-Personal} % Use your personal additional macros. You may edit this file.
	%---The following code defines the title, author, and date of the document.
	\title{Paper 1}
	\date{\today}   % Using \today automatically updates to the document's build date
%----------------------------------
%---------IF YOU WANT TO DEFINE YOUR OWN MACROS, YOU CAN DO SO EITHER IN ../texHead-Proof-Personal.tex OR FROM HERE ...

%---------... TO HERE

\author{PSEUDONYM} %%%%%%%% EDIT THIS LINE. This should be your pseudonym from practice proof 3. You can find it in the feedback for that assignment on Canvas. If you can't find it, then please email the instructor to ask.

\begin{document}
\maketitle
\thispagestyle{fancy}

%-----------EDIT FROM HERE

\begin{abstract}
	Complete the document to make it readable by an audience of your peers.
	The source file contains some hints and ideas.
	Before submitting, please delete the begin \& end abstract tags and everything between them.
	Make sure you include your PSEUDONYM in the document.
	To submit, compile the paper, and submit the PDF file through Canvas.

	You may work with others when figuring out the proofs, but you should acknowledge your peer collaborators in a comment on the Canvas submission (do not acknowledge them in the document submitted).
	You should also acknowledge any peer tutors, books, web pages or other sources you used in a Canvas comment.
	There is no need to acknowledge the Proofs So Far, or other class materials, but you may like to refer to ``Proposition~1.9 of Proofs So Far'', etc.,\ if you are using theorems we already proved.
	{\color{red}You may \emph{not} share \LaTeX{} source files.}

	This is a challenging assignment!
	You are encouraged to interact with other students, according to the rules above, when constructing your proofs.
	It is OK to submit incomplete solutions, as partial credit is available, particularly for the most difficult proofs.
	Some theorems contain multiple statements, and there is credit available for establishing each claim of the theorem.
\end{abstract}

\section{Mean-spirited} \label{sec:mean-spirited}

\begin{thm} \label{thm:mean-spirited}
	For all $a,b,c>0$,
	$$
		\frac{a^2}{bc} + \frac{b^2}{ca} + \frac{c^2}{ab} \geq 3.
	$$
\end{thm}

\begin{proof}[Invalid proof of theorem~\ref{thm:mean-spirited}]
	Suppose (for a contradiction) that
	$$
		\frac{a^2}{bc} + \frac{b^2}{ca} + \frac{c^2}{ab} < 3.
	$$
	Then this inequality must be true for the particular choice of $a=b=c=1>0$.
	But
	$$
		\frac{1^2}{1\times1} + \frac{1^2}{1\times1} + \frac{1^2}{1\times1} = 1+1+1 = 3 \not< 3.
	$$
	This contradicts our assumption, so the theorem is true.
\end{proof}

\noindent\emph{Discussion}:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% THE ABOVE CLAIMED PROOF IS INCORRECT.
% WRITE A FEW SENTENCES TO EXPLAIN THE ERROR.
%
% 1. Is the theorem true or false. If the theorem is false, can you disprove it?
% 2. Whether or not the theorem is true, is the proof correct or incorrect? If there are any errors in the proof, point them out and, if possible, correct.
% 3. Are there any parts of the proof that could be made more efficient?
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{proof}[Correct proof of theorem~\ref{thm:mean-spirited}]
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% Use the AM-GM inequality.
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{proof}

\section{Rationals can always be expressed as ratios as arbitrary powers{\dots}or can they?}

\noindent\emph{The below claimed theorem and proof may or may not be correct.}

\begin{thm} \label{thm:power-rational}
	For each $m,n\in\NN$, and for every positive $x\in\QQ$, there exist $a,b\in\NN$ such that $x = a^m / b^n$.
\end{thm}

\begin{proof}
	By definition, each positive rational can be expressed as $a^1/b^1$ for some choice of naturals $a,b$.
	Suppose that $x\in\QQ$ is such that $x=a^m/b$ for some $m\in\NN$.
	Then
	$$
		x = \frac{a^{m+1}}{ab} = \frac{(a)^{m+1}}{(ab)^1} = \frac{\alpha^{m+1}}{\beta},
	$$
	using $\alpha=a\in\NN$ and $\beta=ab\in\NN$.
	Hence, by induction on $m$, for every $m\in\NN$, and for every positive $x\in\QQ$, there exist $a,b\in\NN$ such that $x = a^m / b$.

	Now suppose that $x\in\QQ$ is such that $x=a/b^n$ for some $n\in\NN$.
	Then
	$$
		x = \frac{ab}{b^{n+1}} = \frac{(ab)^1}{(b)^{n+1}} = \frac{\alpha}{\beta^{n+1}},
	$$
	using $\alpha=ab\in\NN$ and $\beta=b\in\NN$.
	Hence, by induction on $n$, for every $n\in\NN$, and for every positive $x\in\QQ$, there exist $a,b\in\NN$ such that $x = a / b^n$.

	It follows that for every $m,n\in\NN$, and for every positive $x\in\QQ$, there exist $a,b\in\NN$ such that $x = a^m / b^n$.
\end{proof}

\noindent\emph{Discussion}:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% DISCUSS THE ABOVE CLAIMED THEOREM AND PROOF.
% YOU SHOULD WRITE TWO OR THREE PARAGRAPHS TO DISCUSS THE ISSUES BELOW.
%
% 1. Is the theorem true or false. If the theorem is false, can you disprove it?
% 2. Whether or not the theorem is true, is the proof correct or incorrect? If there are any errors in the proof, point them out and, if possible, correct.
% 3. Are there any parts of the proof that could be made more efficient?
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{An irrootional number}

\begin{defn} \label{defn:rootional}
	The \emph{rootionals} (or \emph{rootional numbers}) are the natural roots of rational numbers.
	They are the answers to the question ``Of what should I multiply $n$ copies to get $x$?'', when $0<x\in\QQ$, and $n\in\NN$.
	The \emph{set of rootionals} is denoted $\mathbb{P}$.
	A real number which is not rootional is called \emph{irrootional}.
\end{defn}

\begin{lem} \label{lem:powers-of-1+sqrt2}
	% THE SYMBOLS $\phi$ AND $\psi$ SHOULD NOT APPEAR ANYWHERE IN THE STATEMENT OF THE THEOREM OR THE PROOF WHEN YOU SUBMIT.
	% REPLACE $\phi$ and $\psi$ WITH EXPLICIT FORMULAE.
	The sequences $(a_n)_{n\in\NN}$, $(b_n)_{n\in\NN}$ given by
	\begin{align*}
		a_1 &= 1 & a_{n+1} &= \phi(a_n,b_n), & n &\in\NN, \\
		b_1 &= 1 & b_{n+1} &= \psi(a_n,b_n), & n &\in\NN,
	\end{align*}
	satisfy both
	$$
		\left(1+\sqrt{2}\right)^n = a_n + b_n \sqrt{2} \qquad\mbox{and}\qquad a_n^2-2b_n^2 = (-1)^n,
	$$
	for all $n\in\NN$.
\end{lem}

\begin{proof}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% First you have to complete the statement of the lemma.
	% This means that you have to replace both $\phi(a_n,b_n)$ and $\psi(a_n,b_n)$ with explicit formulae.
	% There is no need to show how you worked out what should replace $\phi$ and $\psi$, just enter the replacements into the statement of the lemma and then give the proof as if you always had always known what $\phi$ and $\psi$ are.
	% THE SYMBOLS $\phi$ AND $\psi$ SHOULD NOT APPEAR ANYWHERE IN THE STATEMENT OF THE LEMMA OR THE PROOF WHEN YOU SUBMIT.
	%
	% The proof is by induction.
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{proof}

\begin{thm} \label{thm:irrootional-eg}
	The number $1+\sqrt{2}$ is irrootional.
\end{thm}

\begin{proof}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% The proof can begin in a similar way to that in which the proof that $\sqrt{2}\notin\RR$ began.
	% Informed by lemma~\ref{lem:powers-of-1+sqrt2}, try to get rid of all roots so that you have an equation of integers.
	% Later it may help to make use of the some of the results related to the fundamental theorem of arithmetic.
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{proof}

\section{$n$-ary representations of integers}

\begin{defn} \label{defn:n-ary-sequence}
	For any integer $n\geq2$, a sequence $(a_j)_{j\in\NN^0}$ is called \emph{$n$-ary} if
	$$
		\{a_j:j\in\NN\}\subset\{0,1,\ldots,n-1\}.
	$$
\end{defn}

\begin{thm} \label{thm:n-ary-rep-int}
	For each $x\in\NN^0$, and for each integer $n\geq2$, there exists an eventually zero $n$-ary sequence $(a_j)_{j\in\NN^0}$ such that
	$$
		x = \sum_{j=0}^\infty a_j n^j.
	$$
\end{thm}

\begin{proof}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% Look for a similar theorem in the Proofs So Far.
	% You will have to extend the argument a bit.
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{proof}

\end{document}

### 2018-09-09 paper1.tex
Ignore generated pdf and got started on Paper 1

@@
 	\usepackage[a4paper,includeheadfoot,left=35mm,right=35mm,top=00mm,bottom=30mm,headheight=40mm]{geometry} %sets up the margins
-	\input{../texHead-Proof-Standard} % Use the standard texHead for this module. You should not edit this file.
-	\input{../texHead-Proof-Personal} % Use your personal additional macros. You may edit this file.
+	\input{./texHead-Proof-Standard} % Use the standard texHead for this module. You should not edit this file.
+	\input{./texHead-Proof-Personal} % Use your personal additional macros. You may edit this file.
 	%---The following code defines the title, author, and date of the document.
@@
 
-\author{PSEUDONYM} %%%%%%%% EDIT THIS LINE.
+\author{Turisas} %%%%%%%% EDIT THIS LINE.
 This should be your pseudonym from practice proof 3.
@@
 %
+The negation on the Theorem's statement is done incorrectly. 
+The statement is, $\forall a,b,c >0$, 
+$$
+	\frac{a^2}{bc} + \frac{b^2}{ca} + \frac{c^2}{ab} \geq 3.
+$$ 
+The correct negation would then be: there $\exists a,b,c >0$ such that 
+$$
+	\frac{a^2}{bc} + \frac{b^2}{ca} + \frac{c^2}{ab} < 3.
+$$
+The proof by contradiction above is done by giving one counterexample against the negation.
+However, this is not sufficient because you have to show that there are no possible $a,b,$ or $c >0$ that satisfies the property. 
+Therefore, the proof is incorrect.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	\begin{align*}
-		a_1 &= 1 & a_{n+1} &= \phi(a_n,b_n), & n &\in\NN, \\
-		b_1 &= 1 & b_{n+1} &= \psi(a_n,b_n), & n &\in\NN,
+		a_1 &= 1 & a_{n+1} &= a_n+2b_n, & n &\in\NN, \\
+		b_1 &= 1 & b_{n+1} &= a_n+b_n, & n &\in\NN,
 	\end{align*}

### 2018-09-09 paper1.tex
Finished the first question.

@@
 	%
+	From the AM-GM inequality, we know
+	\begin{align*}
+		\frac{a+b+c}{3} \geq \sqrt[3]{abc}. 
+	\end{align*}
+	Because we know $abc$ is a positive number, $\sqrt[3]{abc}$ is also positive. So, we can perform the following,
+	\begin{align*}
+	\frac{(a+b+c)(\sqrt[3]{abc})^2}{3} &\geq abc \\
+	\frac{(a+b+c)}{(abc)^{\frac{1}{3}}} &\geq 3 \\
+	\frac{(a)^{\frac{2}{3}}}{(bc)^{\frac{1}{3}}} + \frac{(b)^{\frac{2}{3}}}{(ac)^{\frac{1}{3}}} + \frac{(c)^{\frac{2}{3}}}{(ab)^{\frac{1}{3}}}&\geq 3 \\
+	\sqrt[3]{\frac{a^2}{bc}}+\sqrt[3]{\frac{b^2}{ac}}+\sqrt[3]{\frac{c^2}{ab}}&\geq 3
+	\end{align*}
+	We know that all terms are positive in the above inequality, so,
+	$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq \sqrt[3]{\frac{a^2}{bc}}+\sqrt[3]{\frac{b^2}{ac}}+\sqrt[3]{\frac{c^2}{ab}}\geq3.$$
+	This implies that 
+	$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq 3 .$$
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-09 paper1.tex
Proved Lemma 4

@@
 	%
+	First, we want to show that the sequence satisfies the first equation,
+	$$\left(1+\sqrt{2}\right)^n = a_n + b_n \sqrt{2}.$$
+	When $n=1$ the equations holds,
+	\begin{align*}
+		\mbox{LHS} = \left(1+\sqrt{2}\right)^1=1+\sqrt{2}\\	
+		\mbox{RHS} = a_1+b_1\sqrt{2}=1+\sqrt{2}.
+	\end{align*}
+	So, $\mbox{LHS} = \mbox{RHS},$ and the equation holds for $n=1$.
+	Assume the equations holds for a particular natural number $n$.
+	Now, we want to show that the equation also holds for $n+1$.
+	From our assumption we know,
+	\begin{align*}
+		\left(1+\sqrt{2}\right)^n &= a_n + b_n \sqrt{2}\\
+		\left(1+\sqrt{2}\right)^n(1+\sqrt{2}) &= (a_n + b_n \sqrt{2})(1+\sqrt{2})\\
+		\left(1+\sqrt{2}\right)^{n+1}&= a_n + a_n\sqrt{2} + b_n\sqrt{2} +2b_n\\
+		\left(1+\sqrt{2}\right)^{n+1}&= (a_n+2b_n) + (a_n+b_n)\sqrt{2}\\
+		\left(1+\sqrt{2}\right)^{n+1} &= (a_{n+1}) + (b_{n+1})\sqrt{2}
+	\end{align*}
+	Hence, the equation holds for $n+1$ when it holds for $n$. 
+	By induction on $n$, the equation holds for all natural number $n$.
+
+	Next, we will show that the following equation also holds for the described sequences:
+	$$a_n^2-2b_n^2 = (-1)^n.$$
+	When $n=1$,
+	\begin{align*}
+	\mbox{LHS} = a_1^2-2b_1^2=1-2=-1\\	
+	\mbox{RHS} = (-1)^1=-1{2}.
+	\end{align*}
+	So $\mbox{LHS} = \mbox{RHS},$ and the equation holds for $n=1.$
+	Now, assume that the equation holds for a particular natural number $n$.
+	We want to show that the equation must also hold for $n+1$.
+	Now, consider
+	\begin{align*}
+		a_{n+1}^2-2b_{n+1}^2 &= (a_n+2b_n)^2-2(b_n+a_n)^2\\
+		&= a_n^2 + 4b_na_n +4b^2_n - 2(b_n^2+2a_nb_n+a_n^2)\\
+		&= 2b_n^2-a^2_n\\
+		&= -1(a^2_n-2b_n^2).
+	\end{align*}
+	We know from our induction hypothesis that $a_n^2-2b_n^2 = (-1)^n$, so
+	\begin{align*}
+		a_{n+1}^2-2b_{n+1}^2 &= -1(-1)^n \\
+		a_{n+1}^2-2b_{n+1}^2 &= (-1)^{n+1}.
+	\end{align*}
+	Therefore, the equation holds for $n+1$, if it holds for a natural number $n$. By induction on $n$, the equation holds for all natural number $n$.
+
+	So, it follows that  $(a_n)_{n\in\NN}$, $(b_n)_{n\in\NN}$ satisfy both 
+	$$
+	\left(1+\sqrt{2}\right)^n = a_n + b_n \sqrt{2} \qquad\mbox{and}\qquad a_n^2-2b_n^2 = (-1)^n,
+	$$
+	for all $n\in\NN$.
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-12 paper1.tex
Shortened solution to the 1st proof.
Added a proof for theorem 5

@@
 	%
+	\begin{comment} %My initial longer solution
 		From the AM-GM inequality, we know
@@
 		$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq 3 .$$
+	\end{comment}
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+From the AM-GM inequality, we know
+	\begin{align*}
+		\frac{a^3+b^3+c^3}{3} &\geq \sqrt[3]{a^3b^3c^3} \\
+		{a^3+b^3+c^3} &\geq 3abc.
+	\end{align*}
+	Since we know that $a,b,c > 0$,
+	\begin{align*}
+		\frac{a^3+b^3+c^3}{abc} &\geq 3 \\
+		\frac{a^2}{bc} + \frac{b^2}{ca} + \frac{c^2}{ab} &\geq 3.
+	\end{align*}
 \end{proof}
@@
 	\mbox{LHS} = a_1^2-2b_1^2=1-2=-1\\	
-	\mbox{RHS} = (-1)^1=-1{2}.
+	\mbox{RHS} = (-1)^1=-1.
 	\end{align*}
@@
 	%
-	% The proof can begin in a similar way to that in which the proof that $\sqrt{2}\notin\RR$ began.
-	% Informed by lemma~\ref{lem:powers-of-1+sqrt2}, try to get rid of all roots so that you have an equation of integers.
-	% Later it may help to make use of the some of the results related to the fundamental theorem of arithmetic.
+	 %The proof can begin in a similar way to that in which the proof that $\sqrt{2}\notin\RR$ began.
+	 %Informed by lemma~\ref{lem:powers-of-1+sqrt2}, try to get rid of all roots so that you have an equation of integers.
+	 %Later it may help to make use of the some of the results related to the fundamental theorem of arithmetic.
 	%
+	For a contradiction, let us assume that $1+\sqrt{2}$ is rootional. This means that there exists natural power of $1+\sqrt{2}$ that is equal to a rational number.  So, we can write
+	$$ \left(1+\sqrt{2}\right)^n = \frac{c}{d} $$
+	for natural number $n$ and integers $c,d$. From Lemma 4, we know that \\
+	$\left(1+\sqrt{2}\right)^n = a_n + b_n \sqrt{2}$, so substituting this into the earlier equation yields
+	\begin{align*}
+		a_n + b_n \sqrt{2} &= \frac{c}{d} \\
+		\sqrt{2} &= \frac{\frac{c}{d}-a_n}{b_n} \\
+		\sqrt{2} &= \frac{c-a_nd}{b_nd}
+	\end{align*}
+	We know from the definition of $a_n, b_n$ in Lemma 4 that they are both integers, because the terms in sequences $(a_n)_{n\in\NN}$, $(b_n)_{n\in\NN}$ are constructed simply by adding up previous integer terms, which are initialized at $1$, an integer.
+	Since by assumption $c$ and $d$ are also integers, $\dfrac{c-a_nd}{b_nd}$ is just a fraction of two integers, which is rational.
+So the RHS is rational, but we know that $\sqrt{2}$, which is the LHS, is irrational.
+
+	Therefore, there is a contradiction and $1+\sqrt{2}$ is irrootional
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-14 paper1.tex
Found an easy counterexample for the 2nd proof

@@
 %
-The negation on the Theorem's statement is done incorrectly. 
+Although the theorem is true, the proof is not adequate.
+The negation on the theorem's statement is done incorrectly. 
 The statement is, $\forall a,b,c >0$, 
@@
 The proof by contradiction above is done by giving one counterexample against the negation.
-However, this is not sufficient because you have to show that there are no possible $a,b,$ or $c >0$ that satisfies the property. 
+However, this is not sufficient because you have to show that do not exist $a,b,$ or $c >0$ that satisfies the property. 
 Therefore, the proof is incorrect.
@@
 %
+The theorem is false, because there is a counter example to the theorem. Take $x=2$, and $m=n=2$.
+Then if we assume that the theorem is true, we can write $$2=\left(\frac{a}{b}\right)^2.$$
+Because $a,b$ are positive, 
+	$$\sqrt{2}=\frac{a}{b}.$$
+However, this is impossible because $\dfrac{a}{b}$ is a rational number, but $\sqrt{2}$ is not.
+So the theorem is disproved with a counterexample.
+
+Secondly, the proof is incorrect because it only is able to prove .... 
+If we were to draw a diagram which illustrates the induction of the proof, it would look like this:
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	\end{align*}
-	We know from the definition of $a_n, b_n$ in Lemma 4 that they are both integers, because the terms in sequences $(a_n)_{n\in\NN}$, $(b_n)_{n\in\NN}$ are constructed simply by adding up previous integer terms, which are initialized at $1$, an integer.
-	Since by assumption $c$ and $d$ are also integers, $\dfrac{c-a_nd}{b_nd}$ is just a fraction of two integers, which is rational.
+	We know from the definition of $a_n, b_n$ in Lemma 4 that they are both integers, because the terms in sequences $(a_n)_{n\in\NN}$, $(b_n)_{n\in\NN}$ are constructed simply by adding up previous integer terms, which are initialized at $1$.
+	Since by assumption $c$ and $d$ are also integers, $\dfrac{c-a_nd}{b_nd}$ is just a  quotient of two integers, which defines a rational number.
 So the RHS is rational, but we know that $\sqrt{2}$, which is the LHS, is irrational.
 
-	Therefore, there is a contradiction and $1+\sqrt{2}$ is irrootional
+	Therefore, there is a contradiction and $1+\sqrt{2}$ is irrootional.
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{proof}

### 2018-09-15 paper1.tex
Finished question 2 and added started n-ary

@@
 The theorem is false, because there is a counter example to the theorem. Take $x=2$, and $m=n=2$.
-Then if we assume that the theorem is true, we can write $$2=\left(\frac{a}{b}\right)^2.$$
+Then if we assume that the theorem is true, we can write, with naturals $a,b$ $$2=\left(\frac{a}{b}\right)^2.$$
 Because $a,b$ are positive, 
@@
 However, this is impossible because $\dfrac{a}{b}$ is a rational number, but $\sqrt{2}$ is not.
-So the theorem is disproved with a counterexample.
+So there is a contradiction, and the theorem is disproved.
 
-Secondly, the proof is incorrect because it only is able to prove .... 
-If we were to draw a diagram which illustrates the induction of the proof, it would look like this:
+So, the proof does not prove the theorem, but it was able to prove, through induction, that $x=a^m/b$ works and $x=a/b^n$ works independently. 
+However, it does not follow that for every $m,n\in\NN$, and for every positive $x\in\QQ$, there exist $a,b\in\NN$ such that $x = a^m / b^n$.
 
@@
 	%
+	Let $P(x)$ be the statement of the theorem. $P(0)$ is trivially true because if we write, 
+	$$
+		0 = \sum_{j=0}^\infty a_j n^j,
+	$$
+	the certainly exists an $n$-ary sequence $(a_j)_{j\in\NN^0}$ that is just the infinite sequence with all 0s.
+This sequence would be $n$-ary for every $n$ because for the the smallest $n$, which is 2, $\{0\}\subset\{0,1\}$.
+
+	Now, let $x$ be a natural number such that $x>0$, and suppose that $P(k)$ is true for all integer $k$ such that $0\leq k\leq x$. Now, we want to show that $P(x+1)$ is also true.
+
+	If $x+1$ is divisible by $n$, then $\frac{x+1}{n}\in \NNzero$ and $0\leq\frac{x+1}{n}\leq x$. Since we know that $P(k)$ is true, we know that there exists an $n$-ary sequence such that 
+	$$
+		\frac{x+1}{n} = \sum_{j=0}^\infty a_{\frac{x+1}{n},j} n^j
+	$$
+	where $a_{\frac{x+1}{n},j}$ is the $j$th term in the sequence $a_{\frac{x+1}{n}}$
+	Manipulating this equation yields, 
+	\begin{align*}
+		x+1 &= \sum_{j=0}^\infty a_{\frac{x+1}{n},j} n^{j+1} \\
+		x+1 &= \sum_{j=1}^\infty a_{\frac{x+1}{n},j-1} n^{j}.
+	\end{align*}
+	Now let us define a new sequence $a_{x+1}$ such that $a_{x+1,j} = a_{\frac{x+1}{n},j-1}$
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-15 paper1.tex
Finished 1st draft

@@
 %-----------EDIT FROM HERE
-
-\begin{abstract}
-	Complete the document to make it readable by an audience of your peers.
-	The source file contains some hints and ideas.
-	Before submitting, please delete the begin \& end abstract tags and everything between them.
-	Make sure you include your PSEUDONYM in the document.
-	To submit, compile the paper, and submit the PDF file through Canvas.
-
-	You may work with others when figuring out the proofs, but you should acknowledge your peer collaborators in a comment on the Canvas submission (do not acknowledge them in the document submitted).
-	You should also acknowledge any peer tutors, books, web pages or other sources you used in a Canvas comment.
-	There is no need to acknowledge the Proofs So Far, or other class materials, but you may like to refer to ``Proposition~1.9 of Proofs So Far'', etc.,\ if you are using theorems we already proved.
-	{\color{red}You may \emph{not} share \LaTeX{} source files.}
-
-	This is a challenging assignment!
-	You are encouraged to interact with other students, according to the rules above, when constructing your proofs.
-	It is OK to submit incomplete solutions, as partial credit is available, particularly for the most difficult proofs.
-	Some theorems contain multiple statements, and there is credit available for establishing each claim of the theorem.
-\end{abstract}
 
@@
 \begin{proof}[Correct proof of theorem~\ref{thm:mean-spirited}]
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	%%%%%%%%%%22%%%%%%%%%%%%%%%%%%%%%%%
 	%
@@
 	$$
-	where $a_{\frac{x+1}{n},j}$ is the $j$th term in the sequence $a_{\frac{x+1}{n}}$
+	where $a_{\frac{x+1}{n},j}$ is the $j$th term in the sequence $(a_{\frac{x+1}{n}})_{j\in\NN^0}$
 	Manipulating this equation yields, 
@@
 	\end{align*}
-	Now let us define a new sequence $a_{x+1}$ such that $a_{x+1,j} = a_{\frac{x+1}{n},j-1}$
+	Now, let us define a new sequence $(a_{x+1,j})_{j\in\NN^0}$ such that $a_{x+1,j} = a_{\frac{x+1}{n},j-1}$ for all $j\in \NN$ and $a_{x+1,0} = 0 $. We can then rewrite the previous equation as
+	\begin{align*}
+		x+1 &= 0+ \sum_{j=1}^\infty a_{x+1,j} n^{j} \\
+		x+1 &=  \sum_{j=0}^\infty a_{x+1,j} n^{j}.
+	\end{align*}
+	This new sequence is eventually zero because the original sequence $(a_{\frac{x+1}{n},j})_{j\in\NN^0}$ was eventually zero. 
+	This new sequence is also $n$-ary because $(a_{\frac{x+1}{n},j})_{j\in\NN^0}$ is $n$-ary and we only added another $0$. So we have shown that $P(x+1)$ is true if $x+1$ is divisible by $n$.
+
+	Next, consider the case where $x+1$ is not divisible by $n$. 
+	Then, the quotient remainder theorem states that there exists an integer $r$, $1\leq r\leq n-1$ such that $\frac{x+1-r}{n} \in \NN$. 
+	So, we can write $0\leq\frac{x+1-r}{n}\leq x$. By our inductive hypothesis, we know
+	\begin{align*}
+		\frac{x+1-r}{n} &= \sum_{j=0}^\infty a_{\frac{x+1-r}{n},j} n^{j} \\
+		x+1-r &= \sum_{j=0}^\infty a_{\frac{x+1-r}{n},j} n^{j+1} \\
+		x+1 &= r + \sum_{j=1}^\infty a_{\frac{x+1-r}{n},j-1} n^{j}.
+	\end{align*}
+	Now, we can define a new sequence $(a_{x+1,j})_{j\in\NN^0}$ such that $a_{x+1,j} = a_{\frac{x+1-r}{n},j-1}$ for all $j\in \NN$ and $a_{x+1,0} = r $. We can then rewrite the previous equation as
+	\begin{align*}
+		x+1 &= r + \sum_{j=1}^\infty a_{x+1,j} n^{j}\\
+		x+1 &= \sum_{j=0}^\infty a_{x+1,j} n^{j}.
+	\end{align*}
+	This new sequence is eventually zero because the original sequence  $(a_{\frac{x+1-r}{n},j})_{j\in\NN^0}$ was eventually zero.
+This new sequence is also $n$-ary because  $(a_{\frac{x+1-r}{n},j})_{j\in\NN^0}$ is $n$-ary, and we added an additional term $r$ which is $1\leq r\leq n-1$.
+So we have shown that $P(x+1)$ is also true if $x+1$ is not divisible by $n$.
+
+	Therefore $P(x+1)$ is true for all $n\geq2$. By complete induction on $x$, $P(x)$ is true, and the theorem is proved.
+
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-15 paper1.tex
Finalized the paper 1

@@
 However, this is not sufficient because you have to show that do not exist $a,b,$ or $c >0$ that satisfies the property. 
-Therefore, the proof is incorrect.
+Therefore, the proof is incorrect. However, it was very efficient by showing a simple counterexample, albeit not enough to prove the theorem.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{proof}[Correct proof of theorem~\ref{thm:mean-spirited}]
-	%%%%%%%%%%22%%%%%%%%%%%%%%%%%%%%%%%
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 	%
@@
 So, the proof does not prove the theorem, but it was able to prove, through induction, that $x=a^m/b$ works and $x=a/b^n$ works independently. 
+The proof was very efficient in the induction portion by showing very clearly what the base case, the hypothesis, and the inductive step are without doing so too repetitively.
 However, it does not follow that for every $m,n\in\NN$, and for every positive $x\in\QQ$, there exist $a,b\in\NN$ such that $x = a^m / b^n$.
@@
 		\left(1+\sqrt{2}\right)^{n+1}&= (a_n+2b_n) + (a_n+b_n)\sqrt{2}\\
-		\left(1+\sqrt{2}\right)^{n+1} &= (a_{n+1}) + (b_{n+1})\sqrt{2}
+		\left(1+\sqrt{2}\right)^{n+1} &= (a_{n+1}) + (b_{n+1})\sqrt{2}.
 	\end{align*}
@@
 	$$
-	where $a_{\frac{x+1}{n},j}$ is the $j$th term in the sequence $(a_{\frac{x+1}{n}})_{j\in\NN^0}$
+	where $a_{\frac{x+1}{n},j}$ is the $j$th term in the sequence $(a_{\frac{x+1}{n}})_{j\in\NN^0}.$
 	Manipulating this equation yields, 
@@
 	\end{align*}
-	This new sequence is eventually zero because the original sequence $(a_{\frac{x+1}{n},j})_{j\in\NN^0}$ was eventually zero. 
+	This new sequence is eventually zero because the original sequence $(a_{\frac{x+1}{n},j})_{j\in\NN^0}$ is eventually zero. 
 	This new sequence is also $n$-ary because $(a_{\frac{x+1}{n},j})_{j\in\NN^0}$ is $n$-ary and we only added another $0$. So we have shown that $P(x+1)$ is true if $x+1$ is divisible by $n$.
@@
 	\end{align*}
-	This new sequence is eventually zero because the original sequence  $(a_{\frac{x+1-r}{n},j})_{j\in\NN^0}$ was eventually zero.
+	This new sequence is eventually zero because the original sequence  $(a_{\frac{x+1-r}{n},j})_{j\in\NN^0}$ is eventually zero.
 This new sequence is also $n$-ary because  $(a_{\frac{x+1-r}{n},j})_{j\in\NN^0}$ is $n$-ary, and we added an additional term $r$ which is $1\leq r\leq n-1$.
@@
 
-	Therefore $P(x+1)$ is true for all $n\geq2$. By complete induction on $x$, $P(x)$ is true, and the theorem is proved.
+	Therefore $P(x+1)$ is true for all $n\geq2$ for both cases when $x+1$ is and is not divisible by $n$. By complete induction on $x$, $P(x)$ is true, and the theorem is proved.
 

### 2018-10-01 practice-proofs/PracticeProofs4.tex
Finished Proof 4

@@
 	\title{Practice proofs \#4}
-	\author{Anonymous}
+	\author{Peeranat (ToTo) Tokaeo}
 	\date{\today}   % Using \today automatically updates to the document's build date
@@
 %-----------EDIT FROM HERE
-
-\begin{abstract}
-	\input{PracticeProofsStandardAbstract.tex}
-
-	I fitted the whole model solutions onto a little over 1 page.
-\end{abstract}
 
@@
 	% The intermediate value theorem is also important; if you have not seen it before, then look it up.
+	To prove injectivity, let $0<a<b<1$. Now consider 
+	$f(b) - f(a)$.
+	\begin{align*}
+		f(b) - f(a) &= \frac{1}{1-b} - \frac{1}{b} - \frac{1}{1-a} + \frac{1}{a} \\
+		&= \frac{1-a-1+b}{(1-a)(1-b)} + \frac{b-a}{ab} \\
+		&= \frac{b-a}{(1-a)(1-b)} + \frac{b-a}{ab}\\
+		&= (b-a)\left(\frac{1}{(1-a)(1-b)} + \frac{1}{ab}\right)> 0 
+			\end{align*}
+	We know the last inequality because $b>a$, so $(b-a)>0$.
+So we can conclude that $f(b) >f(a)$ for all $a,b$ such that $0<a<b<1$.
+This means that the function $f$ is strictly increasing, so it will pass the horizontal line test.
+Hence, it is injective.
+
+	To prove surjectivity, let $m$ be a large positive number such that $m>0$.
+Since $\frac{1}{m}$ and $1-\frac{1}{m}$ are both between 0 and 1, we can consider $f(\frac{1}{m})$ and $f(1-\frac{1}{m})$.
+So,
+	\begin{align*}
+	f\left(\frac{1}{m}\right) &= \frac{1}{1-\frac{1}{m}} - \frac{1}		{\frac{1}{m}} \\
+	&= \frac{m}{m-1} - m, 
+\end{align*}		
+and also
+	\begin{align*}
+	f\left(1-\frac{1}{m}\right) &= \frac{1}{1-1+\frac{1}{m}} - \frac{1}{1-\frac{1}{m}}\\
+	&= m - \frac{m}{m-1}.
+	\end{align*}
+	From this, we know that 
+	$$\lim_{m\to\infty} f\left(\frac{1}{m}\right) = \lim_{m\to\infty} \left(\frac{m}{m-1} - m\right) = -\infty,$$ and
+	$$\lim_{m\to\infty} f\left(1-\frac{1}{m}\right) = \lim_{m\to\infty} \left(m - \frac{m}{m-1}\right) = \infty.$$
+	So for every real number $y$, there exists an $m$ such that $ f\left(\frac{1}{m}\right)<y<f\left(1-\frac{1}{m}\right)$, because the function extends from negative infinity to positive infinity.
+Because we know that this function $f$ is continuous, we then also know that every real number $y$ is in the range of $f$ by the intermediate value theorem.
+Hence, the range of $f$ is its codomain, so $f$ is surjective.
+	Because $f$ is injective and surjective, it is bijective.
 	%------------------------------------------%

### 2018-10-01 practice-proofs/PracticeProofs4.tex
Fixed some small errors in proof 4

@@
 	\title{Practice proofs \#4}
-	\author{Peeranat (ToTo) Tokaeo}
+	\author{Anonymous}
 	\date{\today}   % Using \today automatically updates to the document's build date
@@
 
-	To prove surjectivity, let $m$ be a large positive number such that $m>0$.
-Since $\frac{1}{m}$ and $1-\frac{1}{m}$ are both between 0 and 1, we can consider $f(\frac{1}{m})$ and $f(1-\frac{1}{m})$.
-So,
+	To prove surjectivity, let $m$ be positive number such that $m>0$. Since $\frac{1}{m}$ and $1-\frac{1}{m}$ are both between 0 and 1, we can consider $f(\frac{1}{m})$ and $f(1-\frac{1}{m})$. So,
 	\begin{align*}
@@
 	$$\lim_{m\to\infty} f\left(1-\frac{1}{m}\right) = \lim_{m\to\infty} \left(m - \frac{m}{m-1}\right) = \infty.$$
-	So for every real number $y$, there exists an $m$ such that $ f\left(\frac{1}{m}\right)<y<f\left(1-\frac{1}{m}\right)$, because the function extends from negative infinity to positive infinity.
+	So for every real number $y$, there exists an $m$ such that $ f\left(\frac{1}{m}\right)<y<f\left(1-\frac{1}{m}\right)$, because the function extends to negative infinity and to positive infinity.
 Because we know that this function $f$ is continuous, we then also know that every real number $y$ is in the range of $f$ by the intermediate value theorem.

### 2018-10-02 practice-proofs/PracticeProofs5.tex
Correction to practice proofs 5.

@@
 
-\subsection*{Cardinality and subsets}
+We study how cardinality interacts with subsets and power sets.
+
+Recall that we say that two sets are equinumerous if they have the same cardinality.
+The following proposition says that the operation ``take the power set'' preserves equinumerosity.
+
+\begin{prop} \label{prop:PowerSetsPreserveEquinumerosity}
+	Suppose $\# X=\# Y$.
+	Then $\# \power(X)=\# \power(Y)$.
+	Moreover, if $\# X\leq\# Y$, then $\# \power(X)\leq\# \power(Y)$.
+\end{prop}
+
+\begin{proof}
+	%--------------EDIT THIS PART--------------%
+	% Hint: There must be a bijection $f:X\to Y$.
+	% Pick an arbitrary $S\subset X$.
+	% Think about the process of taking the image of $S$ in $f$.
+	% Is that a function of $S$?
+	%------------------------------------------%
+\end{proof}
 
@@
 
-\subsection*{Countable unions of sets}
-
-We study the cardinality of ordinary and disjoint unions of countable sets.
-
-\begin{lem} \label{lem:CountableUnions1}
-	If $\#A=\#B=\aleph_0$, then $\#(A\times B)=\aleph_0$.
-\end{lem}
+\begin{cor} \label{cor:IntersectionCardinality}
+	$\# (X\cap Y) \leq \# X$.
+\end{cor}
 
@@
 	%--------------EDIT THIS PART--------------%
-	% Hint: Direct proof.
-	%------------------------------------------%
-\end{proof}
-
-\begin{prop} \label{prop:CountableUnions2}
-	If, for each $j\in J$, $A_j$ is a nonempty set with cardinality $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
-	$$
-		\# \bigsqcup_{j\in J} A_j = \aleph_0.
-	$$
-\end{prop}
-
-\begin{proof}
-	%--------------EDIT THIS PART--------------%
-	% Hint: Start by recalling the definition of disjoint union. Find separately an injection and a surjection to the disjoint union of interest, and use the CSB theorem.
-	%------------------------------------------%
-\end{proof}
-
-\begin{prop} \label{prop:CountableUnions3}
-	If, for each $j\in J$, $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
-	$$
-		\# \bigcup_{j\in J} A_j \leq \aleph_0.
-	$$
-\end{prop}
-
-\begin{proof}
-	%--------------EDIT THIS PART--------------%
-	% Hint: Direct construction.
-	%------------------------------------------%
-\end{proof}
-
-\subsection*{Cardinality and power sets}
-
-We say that two sets are \emph{equinumerous} if they have the same cardinality. The following proposition says that the operation ``take the power set'' preserves equinumerosity.
-
-\begin{prop} \label{prop:PowerSetsPreserveEquinumerosity}
-	Suppose $\# X=\# Y$. Then $\# \power(X)=\# \power(Y)$. Moreover, if $\# X\leq\# Y$, then $\# \power(X)\leq\# \power(Y)$.
-\end{prop}
-
-\begin{proof}
-	%--------------EDIT THIS PART--------------%
-	% Hint: There must be a bijection $f:X\to Y$. Pick an arbitrary $S\subset X$. Think about the process of taking the image of $S$ in $f$. Is that a function of $S$?
+	% Hint: Use proposition~\ref{prop:SubsetCardinality}.
 	%------------------------------------------%

### 2018-10-03 practice-proofs/EH5.tex

@@
-\subsection*{Cardinality and subsets}
+\begin{prop} \label{prop:PowerSetsPreserveEquinumerosity}
+	Suppose $\# X=\# Y$.
+	Then $\# \power(X)=\# \power(Y)$.
+	Moreover, if $\# X\leq\# Y$, then $\# \power(X)\leq\# \power(Y)$.
+\end{prop}
+
+\hintbox{
+	There must be a bijection $f:X\to Y$.
+	Pick an arbitrary $S\subset X$.
+	Think about the process of taking the image of $S$ in $f$.
+	Is that a function of $S$?
+	Showing injectivity / surjectivity requires you to exploit injectivity / surjectivity of $f$.
+
+	It is probably more efficient to prove the second part of the proposition first.
+}
 
@@
 
-\subsection*{Countable unions of sets}
-
-We study the cardinality of ordinary and disjoint unions of countable sets.
-
-\begin{lem} \label{lem:CountableUnions1}
-	If $\#A=\#B=\aleph_0$, then $\#(A\times B)=\aleph_0$.
-\end{lem}
+\begin{cor} \label{cor:IntersectionCardinality}
+	$\# (X\cap Y) \leq \# X$.
+\end{cor}
 
 \hintbox{
-	Stitch together some bijections that must exist, to produce a useful bijection.
+	Use proposition~\ref{prop:SubsetCardinality}.
+	How do subsets relate to intersections?
 }
-
-\begin{prop} \label{prop:CountableUnions2}
-	If, for each $j\in J$, $A_j$ is a nonempty set with cardinality $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
-	$$
-		\# \bigsqcup_{j\in J} A_j = \aleph_0.
-	$$
-\end{prop}
-
-\hintbox{
-	Start by recalling the definition of disjoint union.
-	Find separately an injection and a surjection to the disjoint union of interest, and use the CSB theorem.
-
-	Can you find a surjection from $\NN\times J$ to the disjoint union?
-
-	Note that we asked for all $A_j$ to be nonempty.
-	What would happen if all (or all but finitely many) $A_j$ were $\emptyset$?
-	This offers a clue to how an injection might be constructed.
-}
-
-\begin{prop} \label{prop:CountableUnions3}
-	If, for each $j\in J$, $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
-	$$
-		\# \bigcup_{j\in J} A_j \leq \aleph_0.
-	$$
-\end{prop}
-
-\hintbox{
-	Direct construction of a surjection from the disjoint union of the previous proposition to this ordinary union.
-}
-
-\subsection*{Cardinality and power sets}
-
-We say that two sets are \emph{equinumerous} if they have the same cardinality. The following proposition says that the operation ``take the power set'' preserves equinumerosity.
-
-\begin{prop} \label{prop:PowerSetsPreserveEquinumerosity}
-	Suppose $\# X=\# Y$. Then $\# \power(X)=\# \power(Y)$. Moreover, if $\# X\leq\# Y$, then $\# \power(X)\leq\# \power(Y)$.
-\end{prop}
-
-\hintbox{
-	There must be a bijection $f:X\to Y$. Pick an arbitrary $S\subset X$.
-	Think about the process of taking the image of $S$ in $f$.
-	Is that a function of $S$? Showing injectivity / surjectivity requires you to exploit injectivity / surjectivity of $f$.
-
-	It is probably more efficient to prove the second part first.
-}

### 2018-10-04 practice-proofs/PracticeProofs5.tex
Finished practice proof 5

@@
 
-\begin{abstract}
-	\input{PracticeProofsStandardAbstract.tex}
-
-	I fitted the whole model solutions onto $1.5$ pages.
-\end{abstract}
-
 We study how cardinality interacts with subsets and power sets.
@@
 	% Is that a function of $S$?
+	If $\# X=\# Y$, then there exists a bijection $f:X\to Y$.	
+	Let us define a function $g: \power(X) \to \power(Y)$ by $g(S) = \{f(x): x \in S\}$.
+	Suppose $S, T \subset X$ such that $S \neq T$. 
+	If $g(S)=g(T)$, then $\forall x\in S$, $f(x) \in g(S)$. 
+	But $g(S)=g(T)$, so $f(x) \in g(T)$ also. 
+	This implies that $\forall x\in S$, $\exists y\in T$ such that $f(x)=f(y)$. If we know that $f$ is injective, then $x=y$. This means that $\forall x\in S,$  $x\in T \implies S \subset T$.
+
+	To show that $T \subset S$, we make the same assumptions. If $g(T)=g(S)$, then $\forall x\in T$, $f(x) \in g(T)$. 
+	But $g(T)=g(S)$ so $f(x), \in g(S)$ also. 
+	This implies that $\forall x\in T$, $\exists y\in S$ such that $f(x)=f(y)$. If we know that $f$ is injective, then $x=y$. This means that $\forall x\in T,$  $x\in S \implies T \subset S$.
+
+	So we have shown that, given that $f$ is injective, $g(S)=g(T)$ implies $S=T$, which means that $g$ is an injection. So, the second part of the theorem is proved.
+
+	To show that $g$ is also surjective and hence a bijection, let $T$ be an arbitrary element of $\power(Y)$, that is $T \subset Y$.
+To show surjectivity, we just need to find $S \in \power(X)$ such that $g(S)=T$.
+Let us define $S=\{f^{-1}(y):y\in T\}$.
+The existence of $f^{-1}: Y \to X$ is guaranteed because we know that $f$ is a bijection.
+Applying $g$ to this defined $S$ yields,
+	\begin{align*}
+		g(S) &= \{f(f^{-1}(y)):y\in T\}\\
+		&= \{y:y\in T\} \\
+		&= T
+	\end{align*}
+	So $g$ is surjective and injective, and therefore $\# \power(X)=\# \power(Y)$.
 	%------------------------------------------%
@@
 	%--------------EDIT THIS PART--------------%
+	Suppose $X\subset Y$ and $x \in X$. Let us define a function $f: X\to Y$ in the following way: $f(x) = x$. Since each $x$ is in $X$, each $x$ is also in $Y$.
+
+	To show that $f$ is injective, suppose there exists $x_1,x_2 \in X$ such that $x_1 \neq x_2$.
+If $f(x_1) = f(x_2)$, then $x_1=f(x_1) = f(x_2)=x_2$, which is a contradiction to our assumption.
+Hence, $f(x_1) = f(x_2) \implies x_1 = x_2$ and $f$ is injective.
+So, by definition of injectivity, $\# X\leq \# Y$.
 	% Hint: Directly construct an injection.
@@
 	% Hint: Use proposition~\ref{prop:SubsetCardinality}.
+	Because $(X\cap Y)$ is a subset of $X$, Proposition 2 tells us that $\# (X\cap Y) \leq \# X$.
 	%------------------------------------------%

### 2018-10-08 practice-proofs/PracticeProofs6.tex
Finished proof 6

@@
 
-\begin{abstract}
-	\input{PracticeProofsStandardAbstract.tex}
-
-	I fitted the whole model solutions onto 1 page.
-\end{abstract}
-
 We study the cardinality of ordinary and disjoint unions of countable sets.
@@
 	% Hint: Direct proof.
+	We know that $\#A=\#B=\aleph_0=\#\NN$. So $\#(A\times B) = \#A \times \#B = \#\NN \times \#\NN = \#(\NN \times \NN) = \aleph_0$. Hence, $\#(A\times B)=\aleph_0$.
 	%------------------------------------------%
@@
 	% Find separately an injection and a surjection to the disjoint union of interest, and use the CSB theorem.
+	To show that an injection exists, consider the set $J$.
+We can easily construct an injection $J \to \bigsqcup_{j\in J} A_j$ where each element in $J$ is mapped to one element in $\bigsqcup_{j\in J} A_j$ that has the second term equal to that $J$.
+	It is guaranteed that at least one such element exists because $A_j$ is a nonempty set for all $j$.
+Because $\aleph_0 = \#J \leq \# \bigsqcup_{j\in J} A_j$, we know $\aleph_0 \leq \# \bigsqcup_{j\in J} A_j$.
+
+	Now to show that there is a surjection from the naturals to $\bigsqcup_{j\in J} A_j$, consider the set $\NN \times J$. 
+	We can map each element of $\NN \times J$ to $\bigsqcup_{j\in J} A_j$ that shares the same second element. 
+	For every specific $j \in J$, there are more or equal number of elements that has $j$ as its second term in $\NN \times J$ than in $\bigsqcup_{j\in J} A_j$, because $\aleph_0\geq\#A_j$.
+Therefore, there certainly exists a surjection from $\NN \times J$ to $\bigsqcup_{j\in J} A_j$.
+This means that $\aleph_0 = \# \NN \times J \geq \# \bigsqcup_{j\in J} A_j$ and also from injection that $\aleph_0 \leq \# \bigsqcup_{j\in J} A_j$.
+
+	So, $\# \bigsqcup_{j\in J} A_j = \aleph_0$.
 	%------------------------------------------%
@@
 	% Hint: Direct construction.
+	Consider the disjoint union $\bigsqcup_{j\in J} A_j$. We can define a function $f: \bigsqcup_{j\in J} A_j \to \bigcup_{j\in J} A_j$ such that $f(a,j) = a$ where $a \in \bigcup_{j\in J} A_j$. 
+	This function is clearly surjective because every element in the union is also an element in the disjoint union, if we remove the second index term.
+So, we have defined $f$ to essentially remove the second index term of each element of $\bigsqcup_{j\in J} A_j$.
+
+	So, $\aleph_0 = \#\bigsqcup_{j\in J} A_j \geq \# \bigcup_{j\in J} A_j$, which implies $\# \bigcup_{j\in J} A_j \leq \aleph_0$.
 	%------------------------------------------%
